---
title: "Your Document Title"
author: "Document Author"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

##Problem Set 1


###Solution

1)  Each row/column is independent therefore, the rank of the matrix A is 4.  This can be calculated in R as follows

```{r}
A <- cbind(c(1,-1,0,5),c(2,0,1,4), c(3,1,-2,-2),c(4,3,1,-3))
A
Ans <- qr(A)
RankA <- Ans$rank
RankA
```

2)  For a mxn matrix if m > n, the maximum rank is n.
    Assuming the matrix  is non-zero, the minimum rank is 1.
    

3)  The rank of the matrix B is 1.  The first column is independent.  The second is twice the first column and therefore not independent.  The third column is half the second column and therefore also not independent.

```{r}
B <- cbind(c(1,3,2), c(2,6,4), c(1,3,2))
B
Ans <- qr(B)
RankB <- Ans$rank
RankB
```

##Problem Set 2

###Solution

The characteristic polynomial is determined as follows:

$A = \begin{bmatrix} 1 & 2 & 3 \\ 0 & 4 & 5 \\ 0 & 0 & 6\end{bmatrix}$

$det\begin{Bmatrix} \lambda \begin{bmatrix} 1 & 0 & 0 \\ 0 & 1 & 0 \\ 0 & 0 & 1 \end{bmatrix} - \begin{bmatrix} 1 & 2 & 3 \\ 0 & 4 & 5 \\ 0 & 0 & 6\end{bmatrix} = 0 \end{Bmatrix}$

$det \begin{bmatrix} \lambda - 1 & 2 & 3 \\ 0 & \lambda - 4 & 5 \\ 0 & 0 & \lambda - 6 \end{bmatrix} = 0$

$(\lambda-1)[(\lambda - 4)(\lambda - 6) - 0]-2(0)+3(0) = 0$

$(\lambda - 1)(\lambda^2 - 10\lambda +24) = 0$

$\lambda^3 - 11\lambda^2+34\lambda-24 = 0$   => This is the characteristic polynomial

####To find eigen values

If we back track to this line 
$(\lambda - 1)(\lambda^2 - 10\lambda +24) = 0$

we can see that $\lambda - 1 = 0$, therefore $\lambda = 1$

The other eigen values can be found by factorising the other part of the equation 
$(\lambda - 1)(\lambda^2 - 10\lambda +24) = 0$  and therefore
$(\lambda^2 - 10\lambda +24) = 0$

By factorisation
$(\lambda - 6)(\lambda - 4) = 0$

Therefore if $\lambda - 6 = 0, \lambda = 6$
and if $\lambda - 4 = 0, \lambda = 4$

The eigen values are 1, 4, and 6

This can also be calculated using R.  See below for calculation of eigen values and vectors.
```{r}
Ab <- cbind(c(1,0,0),c(2,4,0),c(3,5,6))
Ab
Ans <- eigen(Ab)
Ans$values
Ans$vectors
```
