---
title: "Data 605 - Assignment 7"
author: "NNedd"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---

## Question 1


## Question 2


Let X represent the number of years until the machine fails.

### Part A



For geometric distribution:

$f(x) = P(X=x) = (1 - p)^{x-1}p$

In this case:
$P(X=8) = (\frac{9}{10})^7 * \frac{1}{10}$

```{r}

Ans <- dgeom(8,0.1)
Ans
```

Expected value = $\frac{1}{p}$



```{r}
Ans = 1/(1/10)
Ans

```


standard deviation = $\sqrt(1-p)/p^2$


```{r}

Ans = sqrt((1 - (1/10))/((1/10)^2))
Ans
```


###Part B



For exponential distribution

Rate = 1/10

Failure after 8 years:
1 - P(X <= 8)

```{r}
Ans <- 1 - pexp(8,0.1)
Ans
```

Expected Value - 1/0.1

```{r}
Ans = 1/0.1
Ans
```

Standard Deviation = 1/(0.1)^2

```{r}
Ans = 1/((0.1)^2)
Ans
```

### Part C



For Binomial Distribution

X ~ B(8, 0.1)
P(X = 0)

```{r}

Ans = dbinom(0, size=8, prob=0.1) 
Ans

```

Expected Value = n * p

```{r}
Ans = 8 * 0.1
Ans

```



Standard Deviation = $\sqrt(np * (1-p)$

```{r}
Ans = sqrt((8 * 0.1) * (1 - 0.1))
Ans

```


### Part D




X ~ P(0.8)

P(X=0)

```{r}
Ans = ppois(0,0.8)
Ans

```


Expected Value = Variance = 0.8
Standard Deviation:

```{r}
Ans = sqrt(0.8)
Ans

```

