---
title: "Data 605 - Homework 1"
author: "N Nedd"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---


```{r setup_packages, include = FALSE}
require(geometry)
```

## Problem Set One


```{r}
u <- c(0.5,0.5)
v <- c(3,-4)

```


1) The dot product

The dot product is as follows:

(0.5 x 3) + (0.5 x -4) = -0.5

The dot() function in R can also be used

```{r}
dot_prod <- dot(u,v)

```
The dot product is: `r dot_prod`

2) Lengths of u and v

Length of a vector:

$\sqrt(x^2 + y^2)$

Length of u:

$\sqrt(0.5^2 + 0.5^2)$  = 0.707

Length of v:

$\sqrt(3^2 + -4^2)$  = 5

In R:

```{r}
len_u <- sqrt(sum(u * u))

len_v <- sqrt(sum (v * v))

```

The length of U is: `r len_u`

The length of v is: `r len_v`

3) 2u - 3v

2u = (2*0.5, 2*0.5) = (1,1)
3v = (3*3,3*-4) = (9,-12)

2u - 3v = (1-9,1--12) = (-8,13)

In R:

```{r}

comb <- 2*u - 3*v
```

The linear combination is: `r comb`

4) Angle between u and v

cos inverse (dotproduct/product of lengths)

cos inverse ((-0.5)/(0.7071068*5)) = 98.1301 degrees

In R:

```{r}
anglebet <- acos((-0.5)/(0.7071068*5))

#Since answer is in radians, it needs to be converted to degrees
angledegrees <- anglebet *180/pi

```

The angle between u and v is: `r angledegrees` degrees