---
title: "DATA 605 - Assignment 2"
author: "N Nedd"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
    toc: true
    toc_depth: 2
---

## Problem Set 1




### Theory

According to a Khan Academy article about the Properties of Matrix Multiplication (https://www.khanacademy.org/math/precalculus/precalc-matrices/properties-of-matrix-multiplication/a/properties-of-matrix-multiplication), the commutative property does not hold for matrix multiplication.  Therefore, if A and B are two matrices, then AB $\neq$ BA.

###An example

A : 
\[
 \begin{bmatrix}
  1 & 2 \\
  3 & 4 
 \end{bmatrix}
\]

$A^{T}$ = \[
 \begin{bmatrix}
  1 & 3 \\
  2 & 4 
 \end{bmatrix}
\]


$AA^{T}$ = A * $A^{T}$ = 
\[
 \begin{bmatrix}
  1 & 2 \\
  3 & 4 
 \end{bmatrix} * \begin{bmatrix}
  1 & 3 \\
  2 & 4 
 \end{bmatrix} =  \begin{bmatrix}
  1+4 & 3+8 \\
  3+8 & 9+16 
 \end{bmatrix} = \begin{bmatrix}
  5 & 11 \\
  11 & 25 
 \end{bmatrix}
\]


$A^{T}A$ = $A^{T}$ * A = 
\[
 \begin{bmatrix}
  1 & 3 \\
  2 & 4 
 \end{bmatrix} * \begin{bmatrix}
  1 & 2 \\
  3 & 4 
 \end{bmatrix} =  \begin{bmatrix}
  1+9 & 2+12 \\
  2+12 & 4+16 
 \end{bmatrix} = \begin{bmatrix}
  10 & 14 \\
  14 & 20 
 \end{bmatrix}
\]


Clearly, 

\[\begin{bmatrix}
  5 & 11 \\
  11 & 25 
 \end{bmatrix} \neq \begin{bmatrix}
  10 & 14 \\
  14 & 20 
 \end{bmatrix}\]
 
 
 In R:
 

$AA^{T}$
```{r}

matrixA <- matrix(c(1,3,2,4), nrow=2, ncol=2)
matrixA

transposeA <- t(matrixA)
transposeA

AtransposeA <- matrixA %*% transposeA
AtransposeA

```

 $A^{T}A$

```{r}
transposeAA <- transposeA %*% matrixA
transposeAA
```

The two values are not equal


2) The condition $A^{T}A$ = $AA^{T}$ is statisfied if A the matrix is a symmetric matrix since in a symmetric matrix $A = A^{T}$.  




###Problemset 2


#### The function

```{r}
myMatrixFactor <- function(A, n)
{
  for(i in 1:n)
{
  #Upper Triangular matrix
  for(k in i:n)
  {
    total <- 0
    for(j in 1:i)
    {
      total <- total + lowerA[i,j] * upperA[j,k]
    }
    upperA[i,k] <- A[i,k] - total
  }
  
  #Lower triangular matrix
  for(k in i: n)
  {
    if(i==k)
    {
      lowerA[i,i] <- 1
    }
    else
    {
      total <- 0
      for(j in 1:i)
      {
        total <- total + lowerA[k,j]*upperA[j,i]
      }
      lowerA[k,i] <- (A[k,i] - total)/ upperA[i,i]
    }
  }
  
  }
  
  list1 <- list()
  
  list1[[1]] <- A
  list1[[2]] <- lowerA
  list1[[3]] <- upperA
  return (list1)
}
```


#### CAlling the function
```{r}

lowerA <- matrix(0,3,3)
upperA <- matrix(0,3,3)

#Define test matrix

n <- 3
Testmatrix <- matrix(c(2,-4,-4,-1,6,-2,-2,3,8), nrow=3, ncol=3)

#Call Function
Ans <- myMatrixFactor(Testmatrix,3)





```


The Results are as follows:

The original matrix is:

```{r}
Testmatrix
```

The lower triangular matrix (L) is: 

```{r}
Ans[[2]]
```

The upper triangular matrix (U) is:

```{r}
Ans[[3]]
```


To prove:

```{r}
Checkans <- Ans[[2]] %*% Ans[[3]]

Checkans
```

Therefore A = LU

