---
title: "Data 605 - Assignment 4"
author: "N Nedd"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---


## Problem Set 1

The Matrix A is defined below:
```{r}
A <- matrix(c(1,-1,2,0,3,4), nrow=2)
A
```

Using R built-in functions, the transpose of A is found
```{r}
transpA <- t(A)
transpA

```

X is calculated
```{r}
X <- A %*% transpA
X
```

Y is calculated
```{r}
Y <- transpA %*% A
Y
```

The Eigen Values & Vectors of X are calculated using R built in function
```{r}
eigenX <- eigen(X)
```

THe Eigen Values of X are : `r eigenX$values`

The Eigen vectors of X are
```{r}
eigenX$vectors
```


The Eigen Values and Vectors of Y are calculated using R built in function
```{r}
eigenY <- eigen(Y)

```

The Eigen Values of Y are: `r eigenY$values`


The Eigen Vectors of Y are:
```{r}
eigenY$vectors
```


The SVD values of A are calculated using R built in functions:
```{r}
svdA <- svd(A)

```

The singular values of A are:
```{r}

svdA$d
```

The left singular vectors of A:

```{r}
svdA$u

```
Note that the left singular vectors of A correspond to the eigen vector of X.

The right singular vectors of A:

```{r}
svdA$v

```
Note that the right singular vectors of A correspond to the eigen vectors of Y.


##Problem Set 2

The function
```{r}
myinverse <- function(amatrix)
{
  detA <- det(amatrix)
  #The function assumes a 3 x 3 matrix
  imatrix <- matrix(,nrow = 3, ncol = 3)
  
 
  
  #The co-factor matrix = The determinants of the submatrix of each element of the matrix
  #The submatrix is determined removing the corresponding row and column of each element of the matrix
  #Must not forget to multiply by -1 to the power of i+j for alternating +/- signs
  for (i in 1:3) {
    for (j in 1:3){
      imatrix[i,j] <- ((-1) ^ (i+j) ) * det(amatrix[-i,-j])
    }}
  
  #Divide the transpose of the co-factor matrix by the Determinant of A to find the inverse
    
  resultmatrix <- t(imatrix)/detA
  
  return(resultmatrix)
}
```


To test:

Matrix:
```{r}
A <- matrix(c(1,2,3,2,1,4,4,2,1), nrow=3)

A
```


Call function



```{r}
B <- myinverse(A)

B
```


Check result:

```{r}
I <- A %*% B

I
```


